Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Added MERT section.
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1646 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\maketitle
\begin{abstract}
We describe the progress we have made in the past year on \textbf{Joshua} \cite{joshua-wmt09}, 
an open source toolkit for parsing based machine translation.
The new functionality includes: 
support for translation grammars with a rich set of syntactic nonterminals,
the ability for external modules to posit constraints on how spans in the input sentence should be translated,  
lattice parsing for dealing with input uncertainty,
a semiring framework that provides a unified way of doing various dynamic programming calculations, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
visualization of the derivation trees, 
and a cleaner pipeline for MT experiments.
\end{abstract}

@@

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
Support for any style of synchronous context free grammar (SCFG)
% instead of just Hiero grammars.  This 
including syntax augment machine translation (SAMT) grammars \cite{samt2006}
\item
Support for external modules to posit translations for spans in the input sentence that constrain decoding   \cite{PBML-2010-Joshua-modules}
\item
Lattice parsing for dealing with input uncertainty, including ambiguous output from speech recognizers or Chinese word segmenters  \cite{dyer-muresan-resnik:2008:ACLMain}
\item
A semiring architecture over hypergraphs that allows many inference operations to be implemented easily and elegantly \cite{li-eisner:2009:EMNLP}
\item
Improvements to decoding through variational decoding and other approximate methods that overcome intractable MAP decoding \cite{variational-decoding-acl09}
\item
Hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}
\item
Visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}
\item
A convenient framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}
\end{itemize}
The sections below give short descriptions for each of these new functions.

@@

>>>>

\maketitle
\begin{abstract}
We describe the progress we have made in the past year on \textbf{Joshua} \cite{joshua-wmt09}, 
an open source toolkit for parsing based machine translation.
The new functionality includes: 
support for translation grammars with a rich set of syntactic nonterminals,
the ability for external modules to posit constraints on how spans in the input sentence should be translated,  
lattice parsing for dealing with input uncertainty,
a semiring framework that provides a unified way of doing various dynamic programming calculations, 
variational decoding for approximating the intractable MAP decoding,
hypergraph-based discriminative training for better feature engineering, 
a parallelized MERT module,
document-level and tail-based MERT,
visualization of the derivation trees, 
and a cleaner pipeline for MT experiments.
\end{abstract}

@@

This paper describes the additions to the toolkit over the past year, which together form the 2.0 release. The software has been heavily used by the authors and several other groups in their daily research, and has been substantially refined since the first release.  The most important new functions in the toolkit are: 
\begin{itemize}
\item
Support for any style of synchronous context free grammar (SCFG)
% instead of just Hiero grammars.  This 
including syntax augment machine translation (SAMT) grammars \cite{samt2006}
\item
Support for external modules to posit translations for spans in the input sentence that constrain decoding   \cite{PBML-2010-Joshua-modules}
\item
Lattice parsing for dealing with input uncertainty, including ambiguous output from speech recognizers or Chinese word segmenters  \cite{dyer-muresan-resnik:2008:ACLMain}
\item
A semiring architecture over hypergraphs that allows many inference operations to be implemented easily and elegantly \cite{li-eisner:2009:EMNLP}
\item
Improvements to decoding through variational decoding and other approximate methods that overcome intractable MAP decoding \cite{variational-decoding-acl09}
\item
Hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}
\item
A parallelization of MERT's computations, and supporting document-level and tail-based optimization \cite{atypical-mert}
\item
Visualization of the derivation trees and hypergraphs \cite{PBML-2010-Joshua-visualization}
\item
A convenient framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}
\end{itemize}
The sections below give short descriptions for each of these new functions.

@@

\section{Minimum Error Rate Training}

\joshua's MERT module optimizes parameter weights so as to maximize performance
on a development set as measuered by an automatic evaluation metric, such as
Bleu \cite{och-mert}.

We have parallelized our MERT module in two ways: parallelizing the computation
of metric scores, and parallelizing the search over parameters. The computation
of metric scores is a computational concern when tuning to a metric that is
slow to compute, such as translation edit rate \cite{snover-etal:2006:ter}.
Since scoring a candidate is independent from scoring any other candidate, we
parallelize this computation using a multi-threaded solution\footnote{Based on
sample code by Kenneth Heafield.}. Similarly, we parallelize the optimization
of the intermediate initial weight vectors, also using a multi-threaded
solution.

Another feature is the module's awareness of document information, and the
capability to perform optimization of {\em document-based} variants of the
automatic metric \cite{atypical-mert}. For example, in document-based Bleu,
a Bleu score is calculated {\em for each document}, and the tuned score is the
average of those document scores. The MERT module can furthermore be instructed
to target a specific subset of those documents, namely the {\em tail} subset,
where only the subset of documents with the lowest document Bleu scores are
considered.\footnote{This feature is of interest to GALE teams, for instance,
since GALE's evaluation criteria place a lot of focus on translation quality of
tail documents.}

More details on the MERT method and the
implementation can be found in \newcite{Zaidan2009}.\footnote{The module
is also available as a standalone application, {\em Z-MERT}, that can be used
with other MT systems. (Software and documentation at: \url{http://cs.jhu.edu/~ozaidan/zmert}.)}
